\documentclass[letterpaper,13pt]{article}

\newlength{\outerbordwidth}

\pagestyle{empty}

\raggedbottom

\raggedright

\usepackage[svgnames]{xcolor}

\usepackage{framed}

\usepackage{tocloft}

%-----------------------------------------------------------

\setlength{\outerbordwidth}{1pt}  % Width of border outside of title bars

\definecolor{shadecolor}{gray}{0.75}  % Outer background color of title bars (0 = black, 1 = white)

\definecolor{shadecolorB}{gray}{0.93}  % Inner background color of title bars

%-----------------------------------------------------------

%Margin setup

\setlength{\evensidemargin}{-0.25in}

\setlength{\headheight}{-0.25in}

\setlength{\headsep}{0in}

\setlength{\oddsidemargin}{-0.25in}

\setlength{\paperheight}{11in}

\setlength{\paperwidth}{8.5in}

\setlength{\tabcolsep}{0in}

\setlength{\textheight}{9.75in}

\setlength{\textwidth}{7in}

\setlength{\topmargin}{-0.3in}

\setlength{\topskip}{0in}

\setlength{\voffset}{0.1in}

%-----------------------------------------------------------

%Custom commands

\newcommand{\resitem}[1]{\item #1 \vspace{-2pt}}

\newcommand{\resheading}[1]{\vspace{8pt}

  \parbox{\textwidth}{\setlength{\FrameSep}{\outerbordwidth}

    \begin{shaded}

\setlength{\fboxsep}{0pt}\framebox[\textwidth][l]{\setlength{\fboxsep}{4pt}\fcolorbox{shadecolorB}{shadecolorB}{\textbf{\sffamily{\mbox{~}\makebox[6.762in][l]{\large #1} \vphantom{p\^{E}}}}}}

    \end{shaded}

  }\vspace{-5pt}

}

\newcommand{\ressubheading}[4]{

\begin{tabular*}{6.5in}{l@{\cftdotfill{\cftsecdotsep}\extracolsep{\fill}}r}

		\textbf{#1} & #2 \\

		\textit{#3} & \textit{#4} \\

\end{tabular*}\vspace{-6pt}}

%-----------------------------------------------------------

\begin{document}

\begin{tabular*}{7in}{l@{\extracolsep{\fill}}r}

\textbf{\Large Addam Hardy} & \textbf{\today} \\

Software Engineer & addam.hardy@gmail.com \\

718B N. Walnut St., Siloam Springs, AR, 72761 &  \\

(808) 640-8169 \\

\end{tabular*}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\resheading{Goal}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\vspace{8pt}

To find a secure position in a small team environment passionate about innovation, communication and test driven development, that is focused on results and progress instead of process. Less a “job” and more a group of close friends that work well together and are driven to push each other past their limits.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\resheading{Education}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{itemize}

\item

	\ressubheading{University of Arkansas}{Fayetteville, AR}{B.Sc Computer Science (current), B.Sc Electrical Engineering (current)}{2010 - 2012(projected)}

\item

	\ressubheading{Defense Language Institute}{Monterey, CA}{A.Arts Korean Language, Korean Basic Course}{2004-2006}

\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\resheading{Skills}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{itemize}

\item {\bf Development:} C/C++, Python, CUDA, JavaScript, Ruby (Rails), Java, FORTRAN, MATLAB

\item {\bf Numerical Analysis:} Optimization, Linear Algebra, ODEs, PDEs, Monte Carlo, Computational Physics, Complex Systems, Iterative Methods, Tomology

\item {\bf Computer Science:} Machine Learning, Data Mining, Parallel Programming, Data Structures, Artificial Intelligence, Operating Systems

\item Discovering and implementing new ideas. Give me an API and a problem and I will figure it out.

\item Diverse background in Math, Computer Science, Physics and Biology allows me to communicate to a wide scientific and general audience and begin contributing to any group immediately.

\item I have worked in many places in a myriad of fields. I can readily learn and adapt to a new discipline, area or environment and start pushing real results quickly.

\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\resheading{Research and Work Experience}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{itemize}

\item

	\ressubheading{Bloomberg LP}{New York, NY}{Financial Software Development Intern}{Summer 2011}

	\begin{itemize}

		\resitem{Developed end-to-end reporting software in \texttt{C++} and \texttt{javascript}}

    \resitem{Implemented statistical models to perform forward and backward portfolio analysis}

	\end{itemize}

\item

	\ressubheading{DOE Joint Genome Institute (Lawrence Berkeley National Lab)}{Walnut Creek, CA}{Researcher in Analysis Group under Dr. Zhong Wang}{Summer 2010}

	\begin{itemize}

		\resitem{Created \textbf{open source} genome validation software tool in \texttt{python} and \texttt{C}}

    \resitem{Used machine learning to mine TBs of genome data efficiently using novel likelihood function}

	\end{itemize}

\item 

	\ressubheading{Los Alamos National Laboratory}{Los Alamos, NM}{Researcher in Metagenomics Group under Dr. Nick Hengartner}{Summer 2009}

	\begin{itemize}

		\resitem{Wrote \textbf{open source} alignment algorithm software tool in \texttt{python}, \texttt{C} and \texttt{CUDA}}

    \resitem{Used statistical models to discover sequence alignments using parallel algorithms on GPUs}

	\end{itemize}

\item

	\ressubheading{Oregon State University}{Corvallis, OR}{Research Assistant under Prof. Malgorzata Peszynska and Prof. Rubin Landau}{2005-2008}

	\begin{itemize}

		\resitem{Finite element analysis with uncertainty and web-based teaching in \texttt{Java}}

	\end{itemize}

\item

	\ressubheading{Max Plank Institute for the Physics of Complex Systems}{Dresden, Germany}{NSF REU Research Assistant under Prof. Steven Tomsovic}{Summer 2007}

	\begin{itemize}

		\resitem{Research on extreme value statistics in \texttt{MATLAB} and \texttt{FORTRAN}}

	\end{itemize}

\item

	\ressubheading{University of California: Davis}{Davis, CA}{NSF REU Research Assistant under Prof. Daniel Cox}{Summer 2006}

	\begin{itemize}

		\resitem{Computational biophysics research as applied to protein folding in \texttt{Java}}

	\end{itemize}

\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\resheading{Selected Open Source Projects and Publications {\mdseries(github.com/addamh)}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{itemize}

\item \ressubheading{ALE: Assembly Likelihood Estimator}{C, Python}{Probabalistic evaluation of genome assemblies}{2010 - Current}

  \begin{itemize}

    \resitem{Uses statistical likelihood function to score and rank genome assemblies}

		\resitem{Publication being prepared for Genome Research}

    \resitem{Presented at several conferences including SIAM Scientific Computing}

	\end{itemize}

\item \ressubheading{Velvetrope}{Python, C, CUDA}{A parallel statistical algorithm for finding homologous regions within sequences}{2009 - 2010}

  \begin{itemize}

		\resitem{Profiled in DEIXIS Magazine, Publication submitted to BMC Bioinformatics}

    \resitem{Presented at several conferences including Supercomputing and Q-bio}

	\end{itemize}

\item \ressubheading{BetaHelix}{Java}{Computes various statistics about a left or right handed beta helix}{2006 - 2007}

\begin{itemize}

		\resitem{Published in Prion: Left handed $\beta$ helix models for mammalian prion fibrils.}

	\end{itemize}


\end{itemize}

\end{document}
